Quantum Hoare Type Theory

### 2020-10-26 ms-paper/ms-paper.tex
Revise examples in appendix B

\subsection{Hadamard basis states}
\begin{lstlisting}[language=QHaskell]
qplus : {\top} r : Qbit {Id(r, |+\>)}
      = do q <= init 0;
           apply H to q;
           return q

qminus : {\top} r : Qbit {Id(r, |-\>)}
       = do q <= init 1;
            apply H to q;
            return q
\end{lstlisting}

@@

\subsection{Bell pair}
\begin{lstlisting}[language=QHaskell]
bell : {\top} (a, b) : (Qbit o* Qbit) {Id(a, b) /\ a \in {|0\>, |1\>}}
     = do qa <- qplus;
          qb <- share qa;
          return (qa, qb)
\end{lstlisting}

\subsection{Testing modular Bell pair}
\begin{lstlisting}[language=QHaskell]
testBell : {\top} (a, b) : (Bit o* Bit) {\top /\ Id(a, b)}
         = do (qa, qb) <- bell;
              return (measure qa, measure qb)
\end{lstlisting}

>>>>

\subsection{Hadamard basis states}
\begin{lstlisting}[language=QHaskell]
qplus : {\top} r : Qbit {r =q |+\>}
      = do q <= init 0;
           q <= apply H to q;
           return q

qminus : {\top} r : Qbit {r =q |-\>}
       = do q <= init 1;
            q <= apply H to q;
            return q
\end{lstlisting}

@@

\subsection{Bell pair}
\begin{lstlisting}[language=QHaskell]
bell00 : {\top} (a, b) : (Qbit o* Qbit) {(a,b) =q |\Phi+\>}
     = do qa <- qplus;
          (qa, qb) <- share qa;
          return (qa, qb)
\end{lstlisting}

\subsection{Testing modular Bell pair}
\todo{TODO: how is classical equality ensured?}
\begin{lstlisting}[language=QHaskell]
testBell : {\top} (a, b) : (Bit o* Bit) {\top /\ a = b}
         = do (qa, qb) <- bell00;
              a <= measure qa;
              b <= measure qb;
              return (a, b)
\end{lstlisting}
